---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggsegCraddock

<!-- badges: start -->
[![R-CMD-check](https://github.com/ggsegverse/ggsegCraddock/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ggsegverse/ggsegCraddock/actions/workflows/R-CMD-check.yaml)
[![r-universe](https://ggsegverse.r-universe.dev/badges/ggsegCraddock)](https://ggsegverse.r-universe.dev/ggsegCraddock)
<!-- badges: end -->

Craddock spatially constrained spectral clustering parcellations for the ggsegverse Ecosystem.

## Installation

```{r, eval = FALSE}
# From r-universe
install.packages("ggsegCraddock", repos = "https://ggsegverse.r-universe.dev")

# From GitHub
# install.packages("remotes")
remotes::install_github("ggsegverse/ggsegCraddock")
```

## Available atlases

| Atlas | Cortical | Subcortical |
|-------|----------|-------------|
| Craddock 200 | `craddock200_cortical()` | `craddock200_subcortical()` |
| ADHD-200 CC200 | `adhd200_200_cortical()` | `adhd200_200_subcortical()` |
| ADHD-200 CC400 | `adhd200_400_cortical()` | `adhd200_400_subcortical()` |

## Craddock 200

```{r craddock200_cortical}
library(ggsegCraddock)
plot(craddock200_cortical())
```

```{r craddock200_subcortical}
plot(craddock200_subcortical())
```

## ADHD-200 CC200

```{r adhd200_200_cortical}
plot(adhd200_200_cortical())
```

## ADHD-200 CC400

```{r adhd200_400_cortical}
plot(adhd200_400_cortical())
```

## Data source

- **Craddock 200**: [NITRC](https://www.nitrc.org/projects/cluster_roi/)
- **ADHD-200 CC200/CC400**: [NITRC](https://www.nitrc.org/frs/?group_id=427)

**Reference**: Craddock RC, et al. (2012). A whole brain fMRI atlas generated via
spatially constrained spectral clustering. *Human Brain Mapping*, 33(8):1914-1928.
[doi:10.1002/hbm.21333](https://doi.org/10.1002/hbm.21333)
