---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.width = 6,
  out.width = "100%",
  fig.retina = 3
)
```

# ggsegCraddock

> **Work in Progress** -- This package is under active development and has not yet been officially released.

Craddock spatially constrained spectral clustering parcellation for the
ggseg ecosystem.

## Installation

We recommend installing the ggseg-atlases through the ggseg
[r-universe](https://ggseg.r-universe.dev/ui#builds):

```{r}
#| label: install-r-universe
#| eval: false
options(repos = c(
  ggseg = "https://ggseg.r-universe.dev",
  CRAN = "https://cloud.r-project.org"
))

install.packages("ggsegCraddock")
```

You can install this package from [GitHub](https://github.com/) with:

```r
# install.packages("pak")
pak::pak("ggseg/ggsegCraddock")
```

## Cortical atlas

```{r}
#| label: cortical
library(ggseg)
library(ggsegCraddock)
library(ggplot2)

ggplot() +
  geom_brain(
    atlas = craddock200_cortical(),
    mapping = aes(fill = label),
    position = position_brain(hemi ~ view),
    show.legend = FALSE
  ) +
  scale_fill_manual(values = craddock200_cortical()$palette, na.value = "grey") +
  theme_void() +
  ggtitle("Craddock 200 cortical parcellation")
```

## Subcortical atlas

```{r}
#| label: subcortical
ggplot() +
  geom_brain(
    atlas = craddock200_subcortical(),
    mapping = aes(fill = label),
    position = position_brain(. ~ view),
    show.legend = FALSE
  ) +
  scale_fill_manual(values = craddock200_subcortical()$palette, na.value = "grey") +
  theme_void() +
  ggtitle("Craddock 200 subcortical parcellation")
```

## Reference

Craddock RC et al. (2012). A whole brain fMRI atlas generated via spatially
constrained spectral clustering. *Human Brain Mapping*, 33(8), 1914-1928.

## Code of Conduct

Please note that the ggsegCraddock project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this
project, you agree to abide by its terms.
