---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 10,
  fig.retina = 3
)
```

# ggsegCraddock

<!-- badges: start -->
[![R-CMD-check](https://github.com/ggsegverse/ggsegCraddock/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ggsegverse/ggsegCraddock/actions/workflows/R-CMD-check.yaml)
[![r-universe](https://ggseg.r-universe.dev/badges/ggsegCraddock)](https://ggseg.r-universe.dev/ggsegCraddock)
<!-- badges: end -->

Craddock and ADHD-200 spatially constrained spectral clustering parcellations
for the ggseg ecosystem.

Craddock RC, James GA, Holtzheimer PE, Hu XP, & Mayberg HS (2012). A whole
brain fMRI atlas generated via spatially constrained spectral clustering.
*Human Brain Mapping*, 33(8), 1914-1928.

## Installation

We recommend installing the ggseg-atlases through the ggseg
[r-universe](https://ggseg.r-universe.dev/ui#builds):

```{r}
#| label: install-r-universe
#| eval: false
options(repos = c(
  ggseg = "https://ggseg.r-universe.dev",
  CRAN = "https://cloud.r-project.org"
))

install.packages("ggsegCraddock")
```

You can install this package from [GitHub](https://github.com/) with:

```r
# install.packages("pak")
pak::pak("ggsegverse/ggsegCraddock")
```

## Craddock 200 cortical

```{r}
#| label: craddock200-cortical
library(ggseg)
library(ggsegCraddock)
library(ggplot2)

ggplot() +
  geom_brain(
    atlas = craddock200_cortical(),
    mapping = aes(fill = label),
    position = position_brain(hemi ~ view),
    show.legend = FALSE
  ) +
  theme_void()
```

## Craddock 200 subcortical

```{r}
#| label: craddock200-subcortical
ggplot() +
  geom_brain(
    atlas = craddock200_subcortical(),
    mapping = aes(fill = label),
    position = position_brain(. ~ view),
    show.legend = FALSE
  ) +
  theme_void()
```

## ADHD-200 200 cortical

```{r}
#| label: adhd200-200-cortical
ggplot() +
  geom_brain(
    atlas = adhd200_200_cortical(),
    mapping = aes(fill = label),
    position = position_brain(hemi ~ view),
    show.legend = FALSE
  ) +
  theme_void()
```

## ADHD-200 200 subcortical

```{r}
#| label: adhd200-200-subcortical
ggplot() +
  geom_brain(
    atlas = adhd200_200_subcortical(),
    mapping = aes(fill = label),
    position = position_brain(. ~ view),
    show.legend = FALSE
  ) +
  theme_void()
```

## ADHD-200 400 cortical

```{r}
#| label: adhd200-400-cortical
ggplot() +
  geom_brain(
    atlas = adhd200_400_cortical(),
    mapping = aes(fill = label),
    position = position_brain(hemi ~ view),
    show.legend = FALSE
  ) +
  theme_void()
```

## ADHD-200 400 subcortical

```{r}
#| label: adhd200-400-subcortical
ggplot() +
  geom_brain(
    atlas = adhd200_400_subcortical(),
    mapping = aes(fill = label),
    position = position_brain(. ~ view),
    show.legend = FALSE
  ) +
  theme_void()
```

## Data source

Craddock RC, James GA, Holtzheimer PE, Hu XP, & Mayberg HS (2012). A whole
brain fMRI atlas generated via spatially constrained spectral clustering.
*Human Brain Mapping*, 33(8), 1914-1928.
[doi:10.1002/hbm.21333](https://doi.org/10.1002/hbm.21333)
